\Large \bf One-Step, Three-Factor Authentication With Custom-Fit, In-Ear EEG

### 2017-02-15 paper.tex
Minor notes

All best-performing tasks in our best-case set achieved perfect FAR and FRRs, with the exception of P5, whose best-performing task (breathe) had a nonzero FRR.
Breathe appeared as the best task across all participants. Given our training strategy, these results indicate that a given person's breathe task is distinguishable not only among other tasks, but among breathe tasks from other participants.
This task performed about as well as its open-eyes counterpart (Figure \ref{fig:meanByTask}), as did song (eyes open) and sport (though, interestingly, song with eyes closed performed less well).

@@

Finally, our work leaves room for some clear UX improvements.
Future work should try using dry electrodes, commonly found in consumer EEG devices, for comfort and usability.
Future work should also attempt a closed-loop (or online) passthought system, in which users receive immediate feedback on the result of their authentication attempt. A closed-loop BCI system could help us understand how learning effects
on the human side might impact authentication performance, as the human and machine co-adapt through authentication attempts.

>>>>

All best-performing tasks in our best-case set achieved perfect FAR and FRRs, with the exception of P5, whose best-performing task (breathe) had a nonzero FRR.
Breathe appeared as the best task across all participants. Given our training strategy, these results indicate that a given person's breathe task is distinguishable not only among other tasks, but among breathe tasks from other participants (that is, we are not simply picking a unique passthought task for each subject).
This task performed about as well as its open-eyes counterpart (Figure \ref{fig:meanByTask}), as did song (eyes open) and sport (though, interestingly, song with eyes closed performed less well).

@@

Finally, our work leaves room for some clear UX improvements.
Future work should try using dry electrodes, commonly found in consumer EEG devices, for comfort and usability. The electrodes could be grounded to the ear, instead of the forehead.
Additionally, future work could easily place a speaker inside our current custom-fit earbuds to produce working ``hearables'' that can be used as ordinary headphones.

Future work should also attempt a closed-loop (or online) passthought system, in which users receive immediate feedback on the result of their authentication attempt. A closed-loop BCI system could help us understand how learning effects
on the human side might impact authentication performance, as the human and machine co-adapt through authentication attempts.
